Forecasting US Presidential Election Results Using Bayesian Prediction

### 2024-11-03 paper/paper_FV1.qmd
Add files via upload

# Results {#sec-Results}
```{r, fig.width=6, fig.height=3, fig.align='center'}
#| label: fig-figure1
#| warning: false
#| message: false
#| echo:    false
# Visualization for mu
ggplot(data.frame(mu = mu_post), aes(x = mu)) +
  geom_density(fill = "skyblue", alpha = 0.5) +
  labs(
    caption = "Posterior Distribution of mu",
    x = "mu",
    y = "Density"
  ) +
  theme_minimal()
```
@fig-figure1 shows the posterior estimate for the parameter mu shows that the posterior mean is -0.5724523. The 95% credible interval for μ ranges from -1.414763 to 0.5034533, indicating the range within which the true value of μ is likely to fall with 95% probability.
```{r, fig.width=6, fig.height=3, fig.align='center'}
#| label: fig-figure2
#| warning: false
#| message: false
#| echo:    false
ggplot(data.frame(sigma = sigma_post), aes(x = sigma)) +
  geom_density(fill = "lightgreen", alpha = 0.5) +
  labs(
    caption = "Posterior Distribution of sigma",
    x = "sigma",
    y = "Density"
  ) +
  theme_minimal()
```
\newpage
@fig-figure2 shows the parameter sigma, the posterior mean is estimated to be 3.533605. The 95% credible interval for σ extends from 0.8570568 to 10.27852, reflecting the uncertainty around the estimate and providing a range of probable values for σ.

@@

kable(candidate_results, format = "markdown", caption = "Top 4 Candidates Results Table")
```
@tbl-table1 show trump is the most likely candidate to win with an average percentage of 35.5156.
Vote Percentage Distribution
Finally, we visualize the vote percentage distribution of the top candidates.

>>>>

# Results {#sec-Results}
```{r, fig.width=6, fig.height=3, fig.align='center'}
#| label: fig-figure1
#| warning: false
#| message: false
#| echo:    false
# Visualization for mu
ggplot(data.frame(mu = mu_post), aes(x = mu)) +
  geom_density(fill = "skyblue", alpha = 0.5) +
  labs(
    caption = "Posterior Distribution of mu",
    x = "mu",
    y = "Density"
  ) +
  theme_minimal()
```
@fig-figure1 shows the posterior estimate for the parameter mu shows that the posterior mean is -0.5725. The 95% credible interval for μ ranges from -1.4148 to 0.5035, indicating the range within which the true value of μ is likely to fall with 95% probability.
```{r, fig.width=6, fig.height=3, fig.align='center'}
#| label: fig-figure2
#| warning: false
#| message: false
#| echo:    false
ggplot(data.frame(sigma = sigma_post), aes(x = sigma)) +
  geom_density(fill = "lightgreen", alpha = 0.5) +
  labs(
    caption = "Posterior Distribution of sigma",
    x = "sigma",
    y = "Density"
  ) +
  theme_minimal()
```
\newpage
@fig-figure2 shows the parameter sigma, the posterior mean is estimated to be 3.5336. The 95% credible interval for σ extends from 0.8571 to 10.2785, reflecting the uncertainty around the estimate and providing a range of probable values for σ.

@@

kable(candidate_results, format = "markdown", caption = "Top 4 Candidates Results Table")
```
@tbl-table1 show trump is the most likely candidate to win with an average percentage of 35.52.
Vote Percentage Distribution
Finally, we visualize the vote percentage distribution of the top candidates.
